NumLin: Linear Types for Linear Algebra

### 2019-01-12 write-up/paper/lang_and_examples.tex
Update figure captions

\begin{figure}[t]
    \centering
%   \begin{minipage}{.4\textwidth}
%   \centering
    \inputminted[fontsize=\small]{ocaml}{../../examples/kalman.lt}
%   \end{minipage}
%   \begin{minipage}{.4\textwidth}
%   \centering
%   \begin{minted}[linenos,fontsize=\small]{ocaml}
%   let owl_kalman
%       ~sigma
%       ~h
%       ~mu
%       ~r
%       ~data =
%     let open Owl.Mat in
%     let ( * ) = dot in
%     let h' = transpose h in
%     let sigma_h' = sigma * h' in
%     let x = sigma_h' * (inv @@ r + h * sigma_h') in
%     let new_mu = mu + x * (h * mu - data) in
%     let new_sigma = sigma - x * h * sigma in
%     new_sigma, new_mu
%   ;;
%   \end{minted}
%   \end{minipage}
    \caption{Kalman filter: see Figure~\ref{fig:kalman_eqns} for the
        equations this code implements. Line numbers in comments refer to
        equivalent lines in a C implementation
        (Figure~\ref{fig:cblas_kalman}).}\label{fig:lang_kalman}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \inputminted[fontsize=\small]{ocaml}{../../examples/kalman.lt}
    \caption{Kalman filter: see Figure~\ref{fig:kalman_eqns} for the
        equations this code implements and Figure~\ref{fig:cblas_kalman}
        for an equivalent \textsc{Cblas/Lapacke} implementation.}\label{fig:lang_kalman}
\end{figure}
